Get Data

### 2022-02-25 get_data.Rmd
updating with information

#for (i in 1:nrow(get_id)){
for (i in 1:10){ #temporary do a small number

@@

```{r}
# thanks SO for this id for the bad coding on scholar 
p_get_scholar_id <- possibly(get_scholar, otherwise = NA_character_)
scholars <- character(nrow(get_id))
for(i in 1:10) {
  id <- NA
  possibles <- p_get_scholar_id(last_name = get_id$last[i], 
                                first_name = get_id$first[i])

>>>>

for (i in 1:nrow(get_id)){
#for (i in 1:10){ #temporary do a small number

@@

```{r}
# thanks SO for this id for the bad coding on scholar 
p_get_scholar_id <- possibly(get_scholar, otherwise = NA_character_)
scholars <- character(nrow(get_id))
for(i in 39:length(scholars)) {
  id <- NA
  possibles <- p_get_scholar_id(last_name = get_id$last[i], 
                                first_name = get_id$first[i])
